Quasi-consistent efficient meshfree thin shell formulation with penalty-free essential boundary condition enforcement

### 2024-03-27 kinematics.tex
20240322
modfied manuscript

In accordance with the Kirchhoff hypothesis, the thickness of shell will not change, and the deformation related with direction of $\xi^3$ will vanish, i.e. $\epsilon_{3i}=0$. Thus, the rotation $\boldsymbol \theta$ can be rewritten as:
\begin{equation}\label{a3}
\epsilon_{3i} = 0 \Rightarrow
\left \{
\begin{split}
&\boldsymbol \theta \cdot \boldsymbol a_\alpha + \boldsymbol v_{,\alpha} \cdot \boldsymbol a_3 = 0 \\
&\boldsymbol \theta \cdot \boldsymbol a_3 = 0
\end{split}
\right .
\Rightarrow \boldsymbol \theta = - \boldsymbol v_{,\alpha} \cdot \boldsymbol a_3 \boldsymbol a^\alpha
\end{equation}
where $\boldsymbol a^\alpha$'s is the in-plane contravariant base vector, $\boldsymbol a^\alpha \cdot \boldsymbol a_\beta = \delta^\alpha_\beta$, $\delta$ is the Kronecker delta function. The detailed derivation of Eq. \ref{a3} can be found in reference \cite{benzaken2021}.

@@

\subsection{Galerkin weak form for Hu-Washizu principle of complementary energy}
In this study, the Hu-Washizu variational principle of complementary energy \cite{dah-wei1985} was adopted for the development of the proposed analytical approach, the corresponding complementary functional, denoted by $\Pi_C$, is listed as follows:
\begin{equation} \label{functionalc}
\begin{split}
&\Pi_C(\varepsilon_{\alpha\beta},\kappa_{\alpha\beta},N^{\alpha\beta},M^{\alpha\beta}) \\
= &\int_\Omega \frac{h}{2}\varepsilon_{\alpha\beta} C^{\alpha\beta\gamma\eta}\varepsilon_{\gamma\eta}d\Omega 
+ \int_\Omega \frac{h^3}{24}\kappa_{\alpha\beta} C^{\alpha\beta\gamma\eta}\kappa_{\gamma\eta}d\Omega \\
+& \int_\Omega \varepsilon_{\alpha\beta} (N^{\alpha\beta} - h C^{\alpha\beta\gamma\eta} \varepsilon_{\gamma\eta}) d\Omega
+ \int_\Omega \kappa_{\alpha\beta} (M^{\alpha\beta} - \frac{h^3}{12} C^{\alpha\beta\gamma\eta} \kappa_{\gamma\eta}) d\Omega \\
-& \int_{\Gamma_v} \boldsymbol T \cdot \bar{\boldsymbol v} d\Gamma 
+ \int_{\Gamma_\theta} M_{\boldsymbol{nn}} \bar \theta_{\boldsymbol n} d\Gamma - (P \boldsymbol a_3 \cdot \bar{\boldsymbol v})_{\boldsymbol x \in C_w} \\
\end{split}
\end{equation}
where $C^{\alpha\beta\gamma\eta}$'s represent the components of fourth order elasticity tensor with respect to the covariant base and plane stress assumption, and it can be expressed by Young's modulus $E$, Poisson's ratio $\nu$ and the in-plane contravariant metric coefficients $a^{\alpha\beta}$'s, $a^{\alpha\beta} = \boldsymbol a^\alpha \cdot \boldsymbol a^\beta$, as follows: 
\begin{equation}
C^{\alpha\beta\gamma\eta} = \frac{E}{2(1+\nu)}(a^{\alpha\gamma}a^{\beta\eta} + a^{\alpha\eta}a^{\beta\gamma} + \frac{2\nu}{1-\nu} a^{\alpha\beta}a^{\gamma\eta})
\end{equation}
and $N^{\alpha\beta}$, $M^{\alpha\beta}$ are the components of membrane and bending stresses given by:
\begin{equation}
N^{\alpha\beta} = hC^{\alpha\beta\gamma\eta}\varepsilon_{\gamma\eta}, \quad
M^{\alpha\beta} = \frac{h^3}{12}C^{\alpha\beta\gamma\eta}\kappa_{\gamma\eta}
\end{equation}

Essential boundaries on the edges and corners denoted by $\Gamma_v$, $\Gamma_\theta$ and $C_v$ are naturally existed in complementary energy functional, $\bar{\boldsymbol v}$, $\bar \theta_{\boldsymbol n}$ are the corresponding prescribed displacement and normal rotation,respectively. $\boldsymbol T$, $M_{\boldsymbol{nn}}$ and $P$ can be determined by Euler-Lagrange equations of shell problem \cite{benzaken2021} as follows:
\begin{equation}
\boldsymbol T = \boldsymbol T_N + \boldsymbol T_M \; \rightarrow
\begin{cases}
\boldsymbol T_N = \boldsymbol a_\alpha N^{\alpha\beta}n_\beta \\
\boldsymbol T_M = (\boldsymbol a_3 M^{\alpha\beta}s_\alpha n_\beta)_{,\gamma} s^\gamma
+ (\boldsymbol a_3 M^{\alpha\beta})\vert_\beta n_\alpha
\end{cases}
\end{equation}
\begin{equation}
M_{\boldsymbol{nn}} = M^{\alpha\beta}n_\alpha n_\beta
\end{equation}
\begin{equation}
P = -[[M^{\alpha\beta}s_\alpha n_\beta]]
\end{equation}
where $\boldsymbol n = n^\alpha \boldsymbol a_\alpha = n_\alpha \boldsymbol a^\alpha$ and $\boldsymbol s = s^\alpha \boldsymbol a_\alpha = s_\alpha \boldsymbol a^\alpha$ are the outward normal and tangent directions on boundaries. $[[f]]$ is the jump operator defined by:
\begin{equation}
[[f]]_{\boldsymbol x = \boldsymbol x_c} = \lim_{\boldsymbol \epsilon\rightarrow \boldsymbol 0+}(f(\boldsymbol x_c + \boldsymbol \epsilon) - f(\boldsymbol x_c - \boldsymbol \epsilon)), \boldsymbol x_c \in \Gamma
\end{equation}
where $f$ is an arbitrary function on $\Gamma$.

Moreover, the natural boundary conditions should be applied by Lagrangian multiplier method with displacement $\boldsymbol v$ regarded as multiplier. Thus, then the new complementary energy functional namely $\Pi$ is given by:
\begin{equation} \label{functional}
\begin{split}
&\Pi(\boldsymbol v, \varepsilon_{\alpha\beta},\kappa_{\alpha\beta},N^{\alpha\beta},M^{\alpha\beta}) \\
=&\Pi_C(\varepsilon_{\alpha\beta},\kappa_{\alpha\beta},N^{\alpha\beta},M^{\alpha\beta})
+ \int_{\Gamma_M} \theta_{\boldsymbol n} (M_{\boldsymbol{nn}} - \bar M_{\boldsymbol{nn}}) d\Gamma \\
- &\int_{\Gamma_T} \boldsymbol v \cdot (\boldsymbol T - \bar{\boldsymbol T})d\Gamma - \boldsymbol v \cdot \boldsymbol a_3 (P - \bar{P})_{\boldsymbol x \in C_P}
- \int_\Omega \boldsymbol v \cdot (\boldsymbol b - \bar{\boldsymbol b}) d\Omega 
\end{split}
\end{equation}
where $\bar{\boldsymbol T}$, $\bar M_{\boldsymbol nn}$ and $\bar P$ are the prescribed traction, bending moment and concentrated force on edges $\Gamma_T$, $\Gamma_M$ and corner $C_P$ respectively. All the boundaries meet the following geometric relationships:
\begin{equation}\label{geo}
\begin{cases}
\Gamma=\Gamma_v \cup \Gamma_T \cup \Gamma_\theta \cup \Gamma_M, \quad C = C_v \cup C_P, \\
\Gamma_v \cap \Gamma_T = \Gamma_\theta \cap \Gamma_M = C_v \cap C_P = \varnothing
\end{cases}
\end{equation}
and $\bar{\boldsymbol b}$ stands for the prescribed body force in $\Omega$, $\boldsymbol b$ also can be written based on Euler-Lagrange equations \cite{benzaken2021} as:
\begin{equation}
\boldsymbol b = \boldsymbol b_N + \boldsymbol b_M \rightarrow
\begin{cases}
\boldsymbol b_N = (\boldsymbol a_\alpha N^{\alpha\beta})\vert_\beta \\
\boldsymbol b_M = (\boldsymbol a_3 M^{\alpha\beta})\vert_{\alpha\beta}
\end{cases}
\end{equation}

>>>>

In accordance with the Kirchhoff hypothesis, the thickness of shell will not change, and the deformation related with direction of $\xi^3$ will vanish, i.e. $\epsilon_{3i}=0$. Thus, the rotation $\boldsymbol \theta$ can be rewritten as:
\begin{equation}\label{a3}
\epsilon_{3i} = 0 \Rightarrow
\left \{
\begin{split}
&\boldsymbol \theta \cdot \boldsymbol a_\alpha =- \boldsymbol v_{,\alpha} \cdot \boldsymbol a_3 \\
&\boldsymbol \theta \cdot \boldsymbol a_3 = 0
\end{split}
\right .
\Rightarrow \boldsymbol \theta = - \boldsymbol v_{,\alpha} \cdot \boldsymbol a_3 \boldsymbol a^\alpha
\end{equation}
where $\boldsymbol a^\alpha$'s is the in-plane contravariant base vector, $\boldsymbol a^\alpha \cdot \boldsymbol a_\beta = \delta^\alpha_\beta$, $\delta$ is the Kronecker delta function. The detailed derivation of Eq. \ref{a3} can be found in reference \cite{benzaken2021}.

@@

\subsection{Galerkin weak form for Hu-Washizu principle of complementary energy}
In this study, the Hu-Washizu variational principle of complementary energy \cite{dah-wei1985} was adopted for the development of the proposed analytical approach, the corresponding complementary functional, denoted by $\Pi_C$, is listed as follows:
\begin{equation} \label{functionalc}
\begin{split}
&\Pi_C(\varepsilon_{\alpha\beta},\kappa_{\alpha\beta},N^{\alpha\beta},M^{\alpha\beta}) \\
= &\int_\Omega \frac{h}{2}\varepsilon_{\alpha\beta} C^{\alpha\beta\gamma\eta}\varepsilon_{\gamma\eta}d\Omega 
+ \int_\Omega \frac{h^3}{24}\kappa_{\alpha\beta} C^{\alpha\beta\gamma\eta}\kappa_{\gamma\eta}d\Omega \\
+& \int_\Omega \varepsilon_{\alpha\beta} (N^{\alpha\beta} - h C^{\alpha\beta\gamma\eta} \varepsilon_{\gamma\eta}) d\Omega
+ \int_\Omega \kappa_{\alpha\beta} (M^{\alpha\beta} - \frac{h^3}{12} C^{\alpha\beta\gamma\eta} \kappa_{\gamma\eta}) d\Omega \\
-& \int_{\Gamma_v} \boldsymbol T \cdot \bar{\boldsymbol v} d\Gamma 
+ \int_{\Gamma_\theta} M_{\boldsymbol{nn}} \bar \theta_{\boldsymbol n} d\Gamma - (P \boldsymbol a_3 \cdot \bar{\boldsymbol v})_{\boldsymbol x \in C_w} \\
\end{split}
\end{equation}
where $C^{\alpha\beta\gamma\eta}$'s represent the components of fourth order elasticity tensor with respect to the covariant base and plane stress assumption, and it can be expressed by Young's modulus $E$, Poisson's ratio $\nu$ and the in-plane contravariant metric coefficients $a^{\alpha\beta}$'s, $a^{\alpha\beta} = \boldsymbol a^\alpha \cdot \boldsymbol a^\beta$, as follows: 
\begin{equation}
C^{\alpha\beta\gamma\eta} = \frac{E}{2(1+\nu)}(a^{\alpha\gamma}a^{\beta\eta} + a^{\alpha\eta}a^{\beta\gamma} + \frac{2\nu}{1-\nu} a^{\alpha\beta}a^{\gamma\eta})
\end{equation}
and $N^{\alpha\beta}$, $M^{\alpha\beta}$ represent the components of membrane- and bending- stresses which are given by:
\begin{equation}
N^{\alpha\beta} = hC^{\alpha\beta\gamma\eta}\varepsilon_{\gamma\eta}, \quad
M^{\alpha\beta} = \frac{h^3}{12}C^{\alpha\beta\gamma\eta}\kappa_{\gamma\eta}
\end{equation}

Essential boundaries on the edges and corners denoted by $\Gamma_v$, $\Gamma_\theta$ and $C_v$ are naturally existed in complementary energy functional, and $\bar{\boldsymbol v}$, $\bar \theta_{\boldsymbol n}$ are the corresponding prescribed displacement and normal rotation, respectively. $\boldsymbol T$, $M_{\boldsymbol{nn}}$ and $P$ can be determined by Euler-Lagrange equations of shell problem \cite{benzaken2021} as follows:
\begin{equation}
\boldsymbol T = \boldsymbol T_N + \boldsymbol T_M \; \rightarrow
\begin{cases}
\boldsymbol T_N = \boldsymbol a_\alpha N^{\alpha\beta}n_\beta \\
\boldsymbol T_M = (\boldsymbol a_3 M^{\alpha\beta}s_\alpha n_\beta)_{,\gamma} s^\gamma
+ (\boldsymbol a_3 M^{\alpha\beta})\vert_\beta n_\alpha
\end{cases}
\end{equation}
\begin{equation}
M_{\boldsymbol{nn}} = M^{\alpha\beta}n_\alpha n_\beta
\end{equation}
\begin{equation}
P = -[[M^{\alpha\beta}s_\alpha n_\beta]]
\end{equation}
where $\boldsymbol n = n^\alpha \boldsymbol a_\alpha = n_\alpha \boldsymbol a^\alpha$ and $\boldsymbol s = s^\alpha \boldsymbol a_\alpha = s_\alpha \boldsymbol a^\alpha$ are the outward normal and tangent directions on boundaries. $[[f]]$ is the jump operator defined by:
\begin{equation}
[[f]]_{\boldsymbol x = \boldsymbol x_c} = \lim_{\boldsymbol \epsilon\rightarrow \boldsymbol 0+}(f(\boldsymbol x_c + \boldsymbol \epsilon) - f(\boldsymbol x_c - \boldsymbol \epsilon)), \boldsymbol x_c \in \Gamma
\end{equation}
where $f$ is an arbitrary function on $\Gamma$.

Moreover, the natural boundary conditions should be applied by Lagrangian multiplier method with displacement $\boldsymbol v$ regarded as multiplier. Thus, then the new complementary energy functional namely $\Pi$ is given by:
\begin{equation} \label{functional}
\begin{split}
&\Pi(\boldsymbol v, \varepsilon_{\alpha\beta},\kappa_{\alpha\beta},N^{\alpha\beta},M^{\alpha\beta}) \\
=&\Pi_C(\varepsilon_{\alpha\beta},\kappa_{\alpha\beta},N^{\alpha\beta},M^{\alpha\beta})
+ \int_{\Gamma_M} \theta_{\boldsymbol n} (M_{\boldsymbol{nn}} - \bar M_{\boldsymbol{nn}}) d\Gamma \\
- &\int_{\Gamma_T} \boldsymbol v \cdot (\boldsymbol T - \bar{\boldsymbol T})d\Gamma - \boldsymbol v \cdot \boldsymbol a_3 (P - \bar{P})_{\boldsymbol x \in C_P}
- \int_\Omega \boldsymbol v \cdot (\boldsymbol b - \bar{\boldsymbol b}) d\Omega 
\end{split}
\end{equation}
where $\bar{\boldsymbol T}$, $\bar M_{\boldsymbol nn}$ and $\bar P$ are the prescribed traction, bending moment and concentrated force on the edges $\Gamma_T$, $\Gamma_M$ and corner $C_P$, respectively. All the specified boundaries meet the following geometric relationships:
\begin{equation}\label{geo}
\begin{cases}
\Gamma=\Gamma_v \cup \Gamma_T \cup \Gamma_\theta \cup \Gamma_M, \quad C = C_v \cup C_P, \\
\Gamma_v \cap \Gamma_T = \Gamma_\theta \cap \Gamma_M = C_v \cap C_P = \varnothing
\end{cases}
\end{equation}
and $\bar{\boldsymbol b}$ stands for the prescribed body force in $\Omega$, $\boldsymbol b$ can be written based on Euler-Lagrange equations \cite{benzaken2021} as:
\begin{equation}
\boldsymbol b = \boldsymbol b_N + \boldsymbol b_M \rightarrow
\begin{cases}
\boldsymbol b_N = (\boldsymbol a_\alpha N^{\alpha\beta})\vert_\beta \\
\boldsymbol b_M = (\boldsymbol a_3 M^{\alpha\beta})\vert_{\alpha\beta}
\end{cases}
\end{equation}
